Ecological network control

### 2018-05-21 paper/supp-info.Rmd
Text maximum matching supp info

Our approach to find the minumum number of driver nodes relies on finding maximum matchings. 
We start with a directed network in which the direction of the link represents the direction of control (Figure \@ref(fig:fig-direction-of-control)a). 
We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure \@ref(fig:fig-direction-of-control)b). 
Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node on the left-hand side is connected to at most one node on the right-hand side. 
To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a]. 
Once we have the matching (shown in the Figure \@ref(fig:fig-direction-of-control)b) it is then easy to identify the roles of each node in this representation: nodes on the left-hand side that are connected to a matched (purple) link are superior while those connected to a matched link on the right-hand side are matched. 
This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure \@ref(fig:fig-direction-of-control)c). 
Figure \@ref(fig:fig-direction-of-control)d--f illustrate this approach for a network with bidirectional links.

## Finding a single maximum matching {#one-maximum-matching}
```{r}
drake::loadd(fig_supp_matching)
```

>>>>

## Finding a single maximum matching {#one-maximum-matching}

Our approach to find the minumum number of driver nodes relies on finding maximum matchings. 
We start with a directed network in which the direction of the link represents the direction of control (Figure \@ref(fig:fig-maximum-matching-procedure) left panel). 
We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure \@ref(fig:fig-maximum-matching-procedure) center panel). 
Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node on the left-hand side is connected to at most one node on the right-hand side. 
To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a]. 
Once we have the matching (shown in the Figure \@ref(fig:fig-maximum-matching-procedure) center panel) it is then easy to identify the roles of each node in this representation: nodes on the top-level that are connected to a matched (dark purple) link are superior while those connected to a matched link on the bottom-level are matched. 
This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure \@ref(fig:fig-maximum-matching-procedure) right panel).

```{r}
drake::loadd(fig_supp_matching)
```
